\vfill A Testing Framework for Web Applications

### 2014-02-26 Paper/paper.tex
Incorporate Thesis Meeting edits, mostly just notes for later

%%%%%%%%%%%%%%%%%%%%
%%% Introduction/Motivation
%%% More detailed, but still general, description of problem and why we want to solve it
%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Since the advent of the internet, the web has undergone an impressive evolution from plain-text webpages to the highly stylized and functional pages that we see today. In the last four to six years there has been an explosion of new web technologies that make applications more functional: HTML5, CSS3, WebGL, Touch APIs, Geo-location, and a host of others. \cite{EvolutionOfWeb} In that same time period, the number of global internet users has grown to somewhere around 2.5 billion people. \cite{EvolutionOfWeb} The combination of these new technologies and the ever-increasing usage of the internet has led to a significant growth in the number and complexity of web applications.
Like any piece of software, these web applications ought to be tested in order to determine their correctness and give their users the best experience possible. Unfortunately, web applications are the new kids on the block and there is very little conventional wisdom on how to test them. Their dynamic nature and network communication require a different testing toolkit than their predecessors. In addition, web applications are being produced at an incredible rate and so there's often little time to test.
We can see that this is not a solved problem by looking at some of the biggest web application around. A 2011 study showed that YouTube has at least eight errors, Apple has at least seven, Microsoft at least four, and the list goes on. \cite{ErrorsInTheWild} That may seem like a incredibly small amount for such monoliths, and, honestly, it is fairly small, but those are still errors in the software that ought to be fixed.
What this all boils down to is that there needs to be a framework in place for testing these multi-layer, multi-faceted web applications that is easy to use, quick to develop on, and thorough in its coverage.

@@

\subsubsection{JavaScript}
JavaScript, though not the only scripting language with web use, is the primary language used to compliment HTML when making web applications. It is an interpreted language that is most often associated with client-side functionality, but in recent times has extended to the server-side. JavaScript is a prototype based object oriented scripting language with dynamic typing and first-class functions. Much of JavaScript's popularity stems from this dynamic nature that allows for quick, and often dirty, implementation of features in an often iterative environment.

\subsubsection{Node.JS}
Node.JS, often called simply Node, is a JavaScript API for creating and running servers. ``Node's goal is to provide an easy way to build scalable network programs.'' \cite{Node} Node was created in 2009 and is sponsored by Joyent. Node does not use thread-based networking, instead opting for a single-threaded event loop and non-blocking I/O. Node allows developers to create and control web servers without the need for external software, such as Apache, commonly found in other sites.

@@

@@

There are a number of different types of tests and testing concept, we will just focus on Unit Testing and Continuous Integration.

@@

\subsubsection{Why Testing is Important}
I'm consistently surprised by how few people take testing seriously when it comes to non-trivial applications. Many developers will leave testing to their users, i.e., wait for users to have problems and report them before developers will fix them. This is an issue for a number of reasons, a few of which are: frustrated customers are unlikely to continue using a buggy product and are dissuaded from buying future products from the same developer, certain bugs can be security loopholes that may allow users access to information they shouldn't have, in the worst cases a bug may cause damage to a person or property and the developers would be on the hook.

\subsection{Client/Server Architecture}
Web applications have a user-facing client-side and a ``rear-facing'' (IS THIS THE RIGHT TERM...) server-side.

>>>>

%%%%%%%%%%%%%%%%%%%%
%%% Introduction/Motivation
%%% More detailed, but still general, description of problem and why we want to solve it
%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Since the advent of the internet, the web has undergone an impressive evolution from plain-text webpages to the highly stylized and functional pages that we see today. In the last four to six years there has been an explosion of new web technologies that make applications more functional: HTML5, CSS3, WebGL, Touch APIs, Geo-location, and a host of others. \cite{EvolutionOfWeb} In that same time period, the number of global internet users has grown to somewhere around 2.5 billion people. \cite{EvolutionOfWeb} The combination of these new technologies and the ever-increasing usage of the internet has led to a significant growth in the number and complexity of web applications.
Like any piece of software, these web applications require testing in order to determine their correctness and give their users the best experience possible. Unfortunately, web applications are new and there are no standard practices regarding how to test them. Their dynamic nature and network communication require a different testing toolkit than their predecessors. In addition, web applications are being produced at an incredible rate and so there's a need for rapid testing.

We can see that this is not a solved problem by looking at some of the biggest web application around. A 2011 study showed that YouTube has at least eight errors, Apple has at least seven, Microsoft at least four, and the list goes on. \cite{ErrorsInTheWild} That may seem like a incredibly small amount for such monoliths, and, honestly, it is fairly small, but those are still errors in the software that ought to be fixed.
What this all boils down to is that there needs to be a framework in place for testing these multi-layer, multi-faceted web applications that is easy to use, quick to develop on, and thorough in its coverage.

\subsection{What Has Been Done Already?}
- Info info info

\subsubsection{Why It Is Insufficient}
- No standard
- Info info info

\subsection{Problems Still Faced/Why It's So Hard}
- A lot of products to test against (browsers)
- Asynchronous shennanigans

\subsection{Contributions of This Thesis}
- Framework
- Wade through all the tools currently out there
-- Focus in, no need to have every developer check out all 10000 tools
-- Weigh options

@@

- Talk about GeoLocation

- TIE JS PORTION INTO THIS

% \subsubsection{JavaScript}
JavaScript, though not the only scripting language with web use, is the primary language used to compliment HTML when making web applications. It is an interpreted language that is most often associated with client-side functionality, but in recent times has extended to the server-side. JavaScript is a prototype based object oriented scripting language with dynamic typing and first-class functions. Much of JavaScript's popularity stems from this dynamic nature that allows for quick, and often dirty, implementation of features in an often iterative environment.

- THIS NEEDS TO MOVE OR CHANGE SUBSECTION TO `WEB APPLICATIONS'
\subsubsection{Node.JS}
Node.JS, often called simply Node, is a JavaScript API for creating and running servers. ``Node's goal is to provide an easy way to build scalable network programs.'' \cite{Node} Node was created in 2009 and is sponsored by Joyent. Node does not use thread-based networking, instead opting for a single-threaded event loop and non-blocking I/O. Node allows developers to create and control web servers without the need for external software, such as Apache, commonly found in other sites.

@@

- TIE THIS CLIENT/SERVER STUFF into Web Applications, be specific, not generic
\subsection{Client/Server Architecture}
Web applications have a user-facing client-side and a ``rear-facing'' (IS THIS THE RIGHT TERM...) server-side.

@@

There are a number of different types of tests and testing concept, we will just focus on Unit Testing, Continuous Integration, and Acceptance Testing.

@@

% - CONSIDER REMOVING ALTOGETHER
% \subsubsection{Why Testing is Important}
% I'm consistently surprised by how few people take testing seriously when it comes to non-trivial applications. Many developers will leave testing to their users, i.e., wait for users to have problems and report them before developers will fix them. This is an issue for a number of reasons, a few of which are: frustrated customers are unlikely to continue using a buggy product and are dissuaded from buying future products from the same developer, certain bugs can be security loopholes that may allow users access to information they shouldn't have, in the worst cases a bug may cause damage to a person or property and the developers would be on the hook.
